\huge{\textbf{Gesture Based UI Development}} \\ \LARGE{Research Paper}

### 2021-02-14 paper/main.tex
First section completed - might need to chop it down a bit.

\title{\huge{\textbf{Gesture Based UI Development}} \\
\LARGE{Research Paper}}
\author{John Shields}
\date{February 2021}

@@

\begin{figure}[!ht]
    \caption{Charles Wheatstone’s stereoscope}
    \label{image:stereoscope}
    \centering
    \includegraphics[width=0.5\textwidth]{pics/stereoscope.jpg}
\end{figure}

@@

\begin{figure}[!ht]
    \caption{The Headsight}
    \label{image:Headsight}
    \centering
    \includegraphics[width=0.5\textwidth]{pics/Headsight.jpg}
\end{figure}

In the early 1990s, VR was used to create arcade games that introduced the concept to people. These VR arcade games were followed by the launch of the first consumer VR device named the Sega VR. Sega VR was a home console that included stereo sound and head tracking. These products were unable to catch on due to an overwhelming number of headaches and motion sickness reports when operating them.

@@

\subsection{Gesture Recognition}

@@

>>>>

\title{\huge{\textbf{Gesture Based UI Development}} \\
\LARGE{Research Paper}}
\author{John Shields - G00348436}
\date{February 2021}

@@

\begin{figure}[!ht]
    \caption{Charles Wheatstone’s stereoscope}
    \label{image:stereoscope}
    \centering
    \includegraphics[width=0.6\textwidth]{pics/stereoscope.jpg}
\end{figure}

@@

\begin{figure}[!ht]
    \caption{The Headsight}
    \label{image:Headsight}
    \centering
    \includegraphics[width=0.6\textwidth]{pics/Headsight.jpg}
\end{figure}

In the early 1990s, VR was used to create arcade games that introduced the concept to the public. These VR arcade games were followed by the launch of the first consumer VR device named the Sega VR. Sega VR was a home console that included stereo sound and head tracking. The Sega VR was unable to catch on due to an overwhelming number of headaches and motion sickness reports when operating it.

@@

\subsection{Gesture Recognition}
The invention of touchscreens described earlier has brought Gesture Recognition (GR) to a whole new level. GR’s origins were also discussed earlier, so modern uses of the technologies will be discussed here. GR has been quite prominent in video games. The Nintendo Wii brought GR to gaming’s center stage. The pairing of the Wii remote and the Wii sensor bar indicated the console could register a person’s movements and map them in a 3D computer-generated space. With the PlayStation, Sony soon followed the Wii by bringing out the Move and Eye technology similar to Nintendo’s GR work. Microsoft’s Xbox 360 Kinect camera took GR one step further. Its camera allows the Xbox 360 to recognize and track 20 individual joints of the human body as we groove along to Dance Central songs. 
\cite{ref12}

GR has shown great potential in education. Hui-Mei Hsu (2011) presented a complete analysis on the use of Kinect in education and concluded that it should achieve the expected results, enhance classroom interaction and participation, and improve the way teachers can manipulate multimedia materials during the classes.

Myo is a drastic improvement from other motion control devices that use sensors to track gestures. Myo uses electromyography to interpret electrical signals from the wearer's forearm muscles, map them with movements made by the hand of the wearer, and monitor other instruments with certain gestures. For the Myo, it is not likely to be impaired by factors such as inadequate lighting conditions, space, and obstructions, unlike most GR devices using cameras. 
\cite{ref13}

GR technology will continue to evolve through enhancements and become even more widely used as they are becoming more accessible with these enhancements.

\begin{figure}[!ht]
    \caption{The Myo}
    \label{image:MYO}
    \centering
    \includegraphics[width=0.4\textwidth]{pics/myo.png}
\end{figure}

@@

\bibitem{ref12} Gesture Recognition Blog
\newline
URL: \url{https://blog.iinet.net.au/gesture-recognition/}

\bibitem{ref13} University of Birmingham - Gesture Control Technology
\newline
URL: \url{https://tinyurl.com/y68fdjw7}
